---
title: "SPAN output tsv file visualization"
author: "Chia-Te Wang"
date: '2022-06-28'
output: html_document
---

## Part 1 Setup
```{r}
## Import library
library(tidyverse)
library(VennDiagram)
navy=rgb(25,62,114,maxColorValue = 255)
coral=rgb(234,93,78,maxColorValue = 255)
orange=rgb(242,147,48,maxColorValue = 255)
yellow=rgb(254,212,122,maxColorValue = 255)
purple=rgb(102,103,173,maxColorValue = 255)
aqua=rgb(46,169,176,maxColorValue = 255)
green=rgb(70,168,108,maxColorValue = 255)
grey=rgb(172,188,195,maxColorValue = 255)
require(ggplot2)
require(reshape2)
require(scales)
require(ftplottools)
require(viridis)
require(ggsignif)
require(ggpubr)
require(GGally)
require(FactoMineR)
require(factoextra)
```

## Part 2 Venn Diagram (All count >10 ncsgRNAs)
```{r}
## load data for Omicron comparison
B.1.1.529 = read.delim("../../tsv/B.1.1.529_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
B.1.1.529 <- aggregate(count ~ JS , B.1.1.529, sum)

BA.1 = read.delim("../../tsv/BA.1_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
BA.1 <- aggregate(count ~ JS , BA.1, sum)

BA.2 = read.delim("../../tsv/BA.2_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
BA.2 <- aggregate(count ~ JS , BA.2, sum)

BA.4 = read.delim("../../tsv/BA.4_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
BA.4 <- aggregate(count ~ JS , BA.4, sum)

BA.5 = read.delim("../../tsv/BA.5_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
BA.5 <- aggregate(count ~ JS , BA.5, sum)

## generate venn diagram (Omicron)
Omicron_plot <- venn.diagram(list(B.1.1.529=B.1.1.529$JS,
                      BA.1=BA.1$JS,
                      BA.2=BA.2$JS,
                      BA.4=BA.4$JS,
                      BA.5=BA.5$JS),
                      filename = NULL,
                      main = " ",
                     fill =c("navy","orange","yellow","coral","grey"))
grid.newpage()
grid.draw(Omicron_plot)

## load data for different comparison
# Combine Omcrion data
Omicron = read.delim("../../tsv/Omicron_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Omicron <- aggregate(count ~ JS , Omicron, sum)

Alpha = read.delim("../../tsv/Alpha_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Alpha <- aggregate(count ~ JS , Alpha, sum)

Beta = read.delim("../../tsv/Beta_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Beta <- aggregate(count ~ JS , Beta, sum)

Gamma = read.delim("../../tsv/Gamma_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Gamma <- aggregate(count ~ JS , Gamma, sum)

Delta = read.delim("../../tsv/Delta_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Delta <- aggregate(count ~ JS , Delta, sum)

## generate venn diagram (five variants)
Variant_plot <- venn.diagram(list(Omicron=Omicron$JS,
                                  Beta=Beta$JS,
                                  Alpha=Alpha$JS,
                                  Gamma=Gamma$JS,
                                  Delta=Delta$JS),
                             filename = NULL,
                             main.cex = 1,
                             main = " ",fill=c("navy","orange","yellow","coral","grey"))
grid.newpage()
grid.draw(Variant_plot)
ggsave(file.path("./Figure 3. Profiling of noncanonical subgenomic RNAs form different SARS-CoV-2 variants.pdf"), Variant_plot, width = 21, height = 14.8, units = "cm")
```

## Part 3 Venn Diagram (Top 50 noncanonical sgRNA)
```{r}
## load data for Omicron comparison
B.1.1.529_TOP50 = read.delim("../../tsv/B.1.1.529_Top50.tsv", header= TRUE, sep = "\t")
BA.1_TOP50 = read.delim("../../tsv/BA.1_Top50.tsv", header= TRUE, sep = "\t")
BA.2_TOP50 = read.delim("../../tsv/BA.2_Top50.tsv", header= TRUE, sep = "\t")
BA.4_TOP50 = read.delim("../../tsv/BA.4_Top50.tsv", header= TRUE, sep = "\t")
BA.5_TOP50 = read.delim("../../tsv/BA.5_Top50.tsv", header= TRUE, sep = "\t")

## generate venn diagram (Omicron)
Omicron_plot_50 <- venn.diagram(list(B.1.1.529=B.1.1.529_TOP50$JS,
                      BA.1=BA.1_TOP50$JS,
                      BA.2=BA.2_TOP50$JS,
                      BA.4=BA.4_TOP50$JS,
                      BA.5=BA.5_TOP50$JS),
                     filename = NULL,
                     main = " ",
                     main.cex = 1,
                     fill =c("navy","orange","yellow","coral","grey"))
grid.newpage()
grid.draw(Omicron_plot)
ggsave(file.path("./Figure 6. Profiling of Top 50 noncanonical subgenomic RNAs form different SARS-CoV-2 Omicron lineages.pdf"), Omicron_plot_50, width = 21, height = 14.8, units = "cm")

## load data for different comparison
# Combine Omcrion data
Omicron_TOP50 = read.delim("../../tsv/Omicron_Top50.tsv", header= TRUE, sep = "\t")
Alpha_TOP50 = read.delim("../../tsv/Alpha_Top50.tsv", header= TRUE, sep = "\t")
Beta_TOP50 = read.delim("../../tsv/Beta_Top50.tsv", header= TRUE, sep = "\t")
Gamma_TOP50 = read.delim("../../tsv/Gamma_Top50.tsv", header= TRUE, sep = "\t")
Delta_TOP50 = read.delim("../../tsv/Delta_Top50.tsv", header= TRUE, sep = "\t")

## generate venn diagram (five variants)
Variant_plot_50 <- venn.diagram(list(Omicron=Omicron_TOP50$JS,
                                  Beta=Beta_TOP50$JS,
                                  Alpha=Alpha_TOP50$JS,
                                  Gamma=Gamma_TOP50$JS,
                                  Delta=Delta_TOP50$JS),
                             filename = NULL,
                             main = " ",main.cex = 1,fill=c("navy","orange","yellow","coral","grey"))
grid.newpage()
grid.draw(Variant_plot)
ggsave(file.path("./Top50_Five_Variant_venndiagram.pdf"), Variant_plot_50, width = 21, height = 14.8, units = "cm")
```

## Part 4 Intersection
  ## Five Variants Intersection
```{r}
## Echo intersection 
#https://stackoverflow.com/questions/17108191/how-to-export-proper-tsv
#https://www.r-bloggers.com/2012/06/intersect-for-multiple-vectors-in-r/
Alpha_B.1.1.529=intersect(Alpha_TOP50$JS,B.1.1.529_TOP50$JS)
Alpha_BA.1=intersect(Alpha_TOP50$JS,BA.1_TOP50$JS)
Alpha_BA.2=intersect(Alpha_TOP50$JS,BA.2_TOP50$JS)
Alpha_BA.4=intersect(Alpha_TOP50$JS,BA.4_TOP50$JS)
Alpha_BA.5=intersect(Alpha_TOP50$JS,BA.5_TOP50$JS)
write.table(Alpha_B.1.1.529,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Alpha_B.1.1.529",row.names = FALSE,append = T)
write.table(Alpha_BA.1,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Alpha_BA.1",row.names = FALSE,append = T)
write.table(Alpha_BA.2,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Alpha_BA.2",row.names = FALSE,append = T)
write.table(Alpha_BA.4,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Alpha_BA.4",row.names = FALSE,append = T)
write.table(Alpha_BA.5,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Alpha_BA.5",row.names = FALSE,append = T)

Beta_B.1.1.529=intersect(Beta_TOP50$JS,B.1.1.529_TOP50$JS)
Beta_BA.1=intersect(Beta_TOP50$JS,BA.1_TOP50$JS)
Beta_BA.2=intersect(Beta_TOP50$JS,BA.2_TOP50$JS)
Beta_BA.4=intersect(Beta_TOP50$JS,BA.4_TOP50$JS)
Beta_BA.5=intersect(Beta_TOP50$JS,BA.5_TOP50$JS)
write.table(Beta_B.1.1.529,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Beta_B.1.1.529",row.names = FALSE,append = T)
write.table(Beta_BA.1,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Beta_BA.1",row.names = FALSE,append = T)
write.table(Beta_BA.2,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Beta_BA.2",row.names = FALSE,append = T)
write.table(Beta_BA.4,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Beta_BA.4",row.names = FALSE,append = T)
write.table(Beta_BA.5,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Beta_BA.5",row.names = FALSE,append = T)

Gamma_B.1.1.529=intersect(Gamma_TOP50$JS,B.1.1.529_TOP50$JS)
Gamma_BA.1=intersect(Gamma_TOP50$JS,BA.1_TOP50$JS)
Gamma_BA.2=intersect(Gamma_TOP50$JS,BA.2_TOP50$JS)
Gamma_BA.4=intersect(Gamma_TOP50$JS,BA.4_TOP50$JS)
Gamma_BA.5=intersect(Gamma_TOP50$JS,BA.5_TOP50$JS)
write.table(Gamma_B.1.1.529,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Gamma_B.1.1.529",row.names = FALSE,append = T)
write.table(Gamma_BA.1,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Gamma_BA.1",row.names = FALSE,append = T)
write.table(Gamma_BA.2,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Gamma_BA.2",row.names = FALSE,append = T)
write.table(Gamma_BA.4,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Gamma_BA.4",row.names = FALSE,append = T)
write.table(Gamma_BA.5,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Gamma_BA.5",row.names = FALSE,append = T)

Delta_B.1.1.529=intersect(Delta_TOP50$JS,B.1.1.529_TOP50$JS)
Delta_BA.1=intersect(Delta_TOP50$JS,BA.1_TOP50$JS)
Delta_BA.2=intersect(Delta_TOP50$JS,BA.2_TOP50$JS)
Delta_BA.4=intersect(Delta_TOP50$JS,BA.4_TOP50$JS)
Delta_BA.5=intersect(Delta_TOP50$JS,BA.5_TOP50$JS)
write.table(Delta_B.1.1.529,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Delta_B.1.1.529",row.names = FALSE,append = T)
write.table(Delta_BA.1,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Delta_BA.1",row.names = FALSE,append = T)
write.table(Delta_BA.2,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Delta_BA.2",row.names = FALSE,append = T)
write.table(Delta_BA.4,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Delta_BA.4",row.names = FALSE,append = T)
write.table(Delta_BA.5,file='./intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="Delta_BA.5",row.names = FALSE,append = T)
```
  ## BA.4 and BA.5 Intersection
```{r}
BA.4_BA.5=intersect(BA.4_TOP50$JS,BA.5_TOP50$JS)
write.table(BA.4_BA.5,file='./BA.4_BA.5_intersect_JS.tsv', quote=FALSE, sep='\t', col.names ="BA.4_BA.5",row.names = FALSE,append = T)
```

## Part 5 Noncanonical sgRNA junction site visualization
  ## Generate noncanonical sgRNAs plot (BA.4 BA.5)
```{r}
# Noncanonical sgRNA BA.4 versus BA.5
BA.4 =read.delim("../../tsv/BA.4_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
BA.4$j5=as.numeric(as.character(BA.4$j5))
BA.4$j3=as.numeric(as.character(BA.4$j3))
BA.4$location="BA.4"
BA.4$y=0.05

BA.5 =read.delim("../../tsv/BA.5_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
BA.5$j5=as.numeric(as.character(BA.5$j5))
BA.5$j3=as.numeric(as.character(BA.5$j3))
BA.5$location="BA.5"
BA.5$y=-0.05

Variant=rbind(BA.4,BA.5)

summary = Variant%>%mutate(total=(as.numeric(as.character(count))))%>%group_by(j5,y,location,j3)%>%summarise(n=n(),m=sum(total))

full=ggplot(mapping=aes(x=j5,y=y,xend=j3,yend=y))+
  geom_curve(data=summary%>%filter(location=="BA.4")%>%filter(n>5),lineend = "round",curvature=-0.3,color=grey,size=0.1)+
  geom_curve(data=summary%>%filter(location=="BA.5")%>%filter(n>5),lineend = "round",curvature=0.3,color=grey,size=0.1)+
  scale_alpha_continuous("Number of Samples")+
  ft_theme()+
  scale_x_continuous("Position")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=200,ymin=-0.05,ymax=0.05,color="grey30",fill="grey30")+
  annotate(geom="rect",xmin=200,xmax=13483,ymin=-0.05,ymax=0.05,color="grey50",fill="grey50")+
  annotate(geom="text",x=7000,y=0,color="white",label="ORF1a",fontface='bold')+
  annotate(geom="rect",xmin=13483,xmax=30000,ymin=-0.05,ymax=0.05,color="grey60",fill="grey60")+
  annotate(geom="text",x=17000,y=0,color="white",label="ORF1b",fontface='bold')+
  annotate(geom="rect",xmin=21532,xmax=30000,ymin=-0.05,ymax=0.05,color=navy,fill=navy)+
  annotate(geom="text",x=23500,y=0,color="white",label="S",fontface='bold')+
  annotate(geom="rect",xmin=25361,xmax=30000,ymin=-0.05,ymax=0.05,color=coral,fill=coral)+
  annotate(geom="text",x=25750,y=0,color="white",label="3a",fontface='bold')+
  annotate(geom="rect",xmin=26213,xmax=30000,ymin=-0.05,ymax=0.05,color=green,fill=green)+
  annotate(geom="rect",xmin=26449,xmax=30000,ymin=-0.05,ymax=0.05,color=purple,fill=purple)+
  annotate(geom="text",x=26700,y=0,color="white",label="M",fontface='bold')+
  annotate(geom="rect",xmin=27017,xmax=30000,ymin=-0.05,ymax=0.05,color=yellow,fill=yellow)+
  annotate(geom="rect",xmin=27364,xmax=30000,ymin=-0.05,ymax=0.05,color=orange,fill=orange)+
  annotate(geom="rect",xmin=27864,xmax=30000,ymin=-0.05,ymax=0.05,color=grey,fill=grey)+
  annotate(geom="rect",xmin=28235,xmax=30000,ymin=-0.05,ymax=0.05,color=aqua,fill=aqua)+
  annotate(geom="text",x=28800,y=0,color="white",label="N",fontface='bold')+
  annotate(geom="rect",xmin=29510,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,fill="white",alpha=0.3)+
  geom_point(alpha=0.8,data=summary%>%filter(location=="BA.4")%>%filter(n>5)%>%arrange(n),aes(x=j5,y=0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summary%>%filter(location=="BA.5")%>%filter(n>5),aes(x=j5,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summary%>%filter(location=="BA.4")%>%filter(n>5)%>%arrange(n),aes(x=j3,y=0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summary%>%filter(location=="BA.5")%>%filter(n>5),aes(x=j3,y=-0.05,size=m,color=n))+
  theme(
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    axis.line.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    legend.justification = "center",
    legend.direction = "vertical",
    legend.key.size = unit(0.5, "cm"),
    legend.key.height = unit(0.3, "cm"),
        )+
  scale_color_gradient("Number of\nSamples",low=navy,high=coral,limits= c(5,20))+
  annotate(geom="text",label="BA.5",fontface='bold',x=1000,y=-0.5,color="#4D4845", hjust = 0)+
  annotate(geom="text",label="BA.4",fontface='bold',x=1000,y=0.5,color="#4D4845", hjust = 0)+
  scale_size_continuous("Number of\nReads",limits= c(0,180000))

zoom = full+
  coord_cartesian(xlim=c(22000,30000),ylim=c(-0.2,0.2))+
  annotate(geom="text",x=26330,y=0,color="white",label="E",fontface='bold')+
  annotate(geom="text",x=27170,y=0,color="white",label="6",fontface='bold')+
  annotate(geom="text",x=27600,y=0,color="white",label="7a",fontface='bold')+
  annotate(geom="text",x=28010,y=0,color="white",label="8",fontface='bold')+
  annotate(geom="text",x=29750,y=0,color="white",label="10",fontface='bold')+
  theme(
    legend.position="none",
    axis.title.x = element_blank(),
    panel.background = element_rect(colour="#4D4845"),
    plot.title = element_text(size=10,colour="#4D4845")
  )+ggtitle("Zoom 22000-30000")
```
  ## Generate noncanonical sgRNAs plot (Alpha Omicron)
```{r}
# Noncanonical sgRNA
Alpha =read.delim("../../tsv/Alpha_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Alpha$j5=as.numeric(as.character(Alpha$j5))
Alpha$j3=as.numeric(as.character(Alpha$j3))
Alpha$location="Alpha"
Alpha$y=-0.05

Omicron =read.delim("../../tsv/Omicron_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Omicron$j5=as.numeric(as.character(Omicron$j5))
Omicron$j3=as.numeric(as.character(Omicron$j3))
Omicron$location="Omicron"
Omicron$y=0.05

VariantA=rbind(Alpha,Omicron)

summaryA = VariantA%>%mutate(total=(as.numeric(as.character(count))))%>%group_by(j5,y,location,j3)%>%summarise(n=n(),m=sum(total))

fullA=ggplot(mapping=aes(x=j5,y=y,xend=j3,yend=y))+
  geom_curve(data=summaryA%>%filter(location=="Alpha")%>%filter(n>20),lineend = "round",curvature=0.3,color=grey,size=0.1)+
  geom_curve(data=summaryA%>%filter(location=="Omicron")%>%filter(n>20),lineend = "round",curvature=-0.3,color=grey,size=0.1)+
  scale_alpha_continuous("Number of Samples")+
  ft_theme()+
  scale_x_continuous("Position")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=200,ymin=-0.05,ymax=0.05,color="grey30",fill="grey30")+
  annotate(geom="rect",xmin=200,xmax=13483,ymin=-0.05,ymax=0.05,color="grey50",fill="grey50")+
  annotate(geom="text",x=7000,y=0,color="white",label="ORF1a",fontface='bold')+
  annotate(geom="rect",xmin=13483,xmax=30000,ymin=-0.05,ymax=0.05,color="grey60",fill="grey60")+
  annotate(geom="text",x=17000,y=0,color="white",label="ORF1b",fontface='bold')+
  annotate(geom="rect",xmin=21532,xmax=30000,ymin=-0.05,ymax=0.05,color=navy,fill=navy)+
  annotate(geom="text",x=23500,y=0,color="white",label="S",fontface='bold')+
  annotate(geom="rect",xmin=25361,xmax=30000,ymin=-0.05,ymax=0.05,color=coral,fill=coral)+
  annotate(geom="text",x=25750,y=0,color="white",label="3a",fontface='bold')+
  annotate(geom="rect",xmin=26213,xmax=30000,ymin=-0.05,ymax=0.05,color=green,fill=green)+
  annotate(geom="rect",xmin=26449,xmax=30000,ymin=-0.05,ymax=0.05,color=purple,fill=purple)+
  annotate(geom="text",x=26700,y=0,color="white",label="M",fontface='bold')+
  annotate(geom="rect",xmin=27017,xmax=30000,ymin=-0.05,ymax=0.05,color=yellow,fill=yellow)+
  annotate(geom="rect",xmin=27364,xmax=30000,ymin=-0.05,ymax=0.05,color=orange,fill=orange)+
  annotate(geom="rect",xmin=27864,xmax=30000,ymin=-0.05,ymax=0.05,color=grey,fill=grey)+
  annotate(geom="rect",xmin=28235,xmax=30000,ymin=-0.05,ymax=0.05,color=aqua,fill=aqua)+
  annotate(geom="text",x=28800,y=0,color="white",label="N",fontface='bold')+
  annotate(geom="rect",xmin=29510,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,fill="white",alpha=0.3)+
  geom_point(alpha=0.8,data=summaryA%>%filter(location=="Alpha")%>%filter(n>20)%>%arrange(n),aes(x=j5,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryA%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j5,y=0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryA%>%filter(location=="Alpha")%>%filter(n>20)%>%arrange(n),aes(x=j3,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryA%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j3,y=0.05,size=m,color=n))+
  theme(
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    axis.line.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    legend.justification = "center",
    legend.direction = "vertical",
    legend.key.size = unit(0.5, "cm"),
    legend.key.height = unit(0.3, "cm"),
        )+
  scale_color_gradient("Number of\nSamples",low=navy,high=coral,limits= c(20,80))+
  annotate(geom="text",label="Alpha",fontface='bold',x=1000,y=-0.5,color="#4D4845", hjust = 0)+
  annotate(geom="text",label="Omicron",fontface='bold',x=1000,y=0.5,color="#4D4845", hjust = 0)+
  scale_size_continuous("Number of\nReads",limits= c(0,180000))
```
  ## Generate noncanonical sgRNAs plot (Beta Omicron)
```{r}
# Noncanonical sgRNA
Beta =read.delim("../../tsv/Beta_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Beta$j5=as.numeric(as.character(Beta$j5))
Beta$j3=as.numeric(as.character(Beta$j3))
Beta$location="Beta"
Beta$y=-0.05

Omicron =read.delim("../../tsv/Omicron_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Omicron$j5=as.numeric(as.character(Omicron$j5))
Omicron$j3=as.numeric(as.character(Omicron$j3))
Omicron$location="Omicron"
Omicron$y=0.05

VariantB=rbind(Beta,Omicron)

summaryB = VariantB%>%mutate(total=(as.numeric(as.character(count))))%>%group_by(j5,y,location,j3)%>%summarise(n=n(),m=sum(total))

fullB=ggplot(mapping=aes(x=j5,y=y,xend=j3,yend=y))+
  geom_curve(data=summaryB%>%filter(location=="Beta")%>%filter(n>20),lineend = "round",curvature=0.3,color=grey,size=0.1)+
  geom_curve(data=summaryB%>%filter(location=="Omicron")%>%filter(n>20),lineend = "round",curvature=-0.3,color=grey,size=0.1)+
  scale_alpha_continuous("Number of Samples")+
  ft_theme()+
  scale_x_continuous("Position")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=200,ymin=-0.05,ymax=0.05,color="grey30",fill="grey30")+
  annotate(geom="rect",xmin=200,xmax=13483,ymin=-0.05,ymax=0.05,color="grey50",fill="grey50")+
  annotate(geom="text",x=7000,y=0,color="white",label="ORF1a",fontface='bold')+
  annotate(geom="rect",xmin=13483,xmax=30000,ymin=-0.05,ymax=0.05,color="grey60",fill="grey60")+
  annotate(geom="text",x=17000,y=0,color="white",label="ORF1b",fontface='bold')+
  annotate(geom="rect",xmin=21532,xmax=30000,ymin=-0.05,ymax=0.05,color=navy,fill=navy)+
  annotate(geom="text",x=23500,y=0,color="white",label="S",fontface='bold')+
  annotate(geom="rect",xmin=25361,xmax=30000,ymin=-0.05,ymax=0.05,color=coral,fill=coral)+
  annotate(geom="text",x=25750,y=0,color="white",label="3a",fontface='bold')+
  annotate(geom="rect",xmin=26213,xmax=30000,ymin=-0.05,ymax=0.05,color=green,fill=green)+
  annotate(geom="rect",xmin=26449,xmax=30000,ymin=-0.05,ymax=0.05,color=purple,fill=purple)+
  annotate(geom="text",x=26700,y=0,color="white",label="M",fontface='bold')+
  annotate(geom="rect",xmin=27017,xmax=30000,ymin=-0.05,ymax=0.05,color=yellow,fill=yellow)+
  annotate(geom="rect",xmin=27364,xmax=30000,ymin=-0.05,ymax=0.05,color=orange,fill=orange)+
  annotate(geom="rect",xmin=27864,xmax=30000,ymin=-0.05,ymax=0.05,color=grey,fill=grey)+
  annotate(geom="rect",xmin=28235,xmax=30000,ymin=-0.05,ymax=0.05,color=aqua,fill=aqua)+
  annotate(geom="text",x=28800,y=0,color="white",label="N",fontface='bold')+
  annotate(geom="rect",xmin=29510,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,fill="white",alpha=0.3)+
  geom_point(alpha=0.8,data=summaryB%>%filter(location=="Beta")%>%filter(n>20)%>%arrange(n),aes(x=j5,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryB%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j5,y=0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryB%>%filter(location=="Beta")%>%filter(n>20)%>%arrange(n),aes(x=j3,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryB%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j3,y=0.05,size=m,color=n))+
  theme(
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    axis.line.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    legend.justification = "center",
    legend.direction = "vertical",
    legend.key.size = unit(0.5, "cm"),
    legend.key.height = unit(0.3, "cm"),
        )+
  scale_color_gradient("Number of\nSamples",low=navy,high=coral,limits= c(20,80))+
  annotate(geom="text",label="Beta",fontface='bold',x=1000,y=-0.5,color="#4D4845", hjust = 0)+
  annotate(geom="text",label="Omicron",fontface='bold',x=1000,y=0.5,color="#4D4845", hjust = 0)+
  scale_size_continuous("Number of\nReads",limits= c(0,180000))

#ggsave(file.path("./Beta_Omicron.pdf"), full, width = 20, height = 13, units = "cm")
```
  ## Generate noncanonical sgRNAs plot (Gamma Omicron)
```{r}
# Noncanonical sgRNA
Gamma =read.delim("../../tsv/Gamma_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Gamma$j5=as.numeric(as.character(Gamma$j5))
Gamma$j3=as.numeric(as.character(Gamma$j3))
Gamma$location="Gamma"
Gamma$y=-0.05

Omicron =read.delim("../../tsv/Omicron_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Omicron$j5=as.numeric(as.character(Omicron$j5))
Omicron$j3=as.numeric(as.character(Omicron$j3))
Omicron$location="Omicron"
Omicron$y=0.05

VariantC=rbind(Gamma,Omicron)

summaryC = VariantC%>%mutate(total=(as.numeric(as.character(count))))%>%group_by(j5,y,location,j3)%>%summarise(n=n(),m=sum(total))

fullC=ggplot(mapping=aes(x=j5,y=y,xend=j3,yend=y))+
  geom_curve(data=summaryC%>%filter(location=="Gamma")%>%filter(n>20),lineend = "round",curvature=0.3,color=grey,size=0.1)+
  geom_curve(data=summaryC%>%filter(location=="Omicron")%>%filter(n>20),lineend = "round",curvature=-0.3,color=grey,size=0.1)+
  scale_alpha_continuous("Number of Samples")+
  ft_theme()+
  scale_x_continuous("Position")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=200,ymin=-0.05,ymax=0.05,color="grey30",fill="grey30")+
  annotate(geom="rect",xmin=200,xmax=13483,ymin=-0.05,ymax=0.05,color="grey50",fill="grey50")+
  annotate(geom="text",x=7000,y=0,color="white",label="ORF1a",fontface='bold')+
  annotate(geom="rect",xmin=13483,xmax=30000,ymin=-0.05,ymax=0.05,color="grey60",fill="grey60")+
  annotate(geom="text",x=17000,y=0,color="white",label="ORF1b",fontface='bold')+
  annotate(geom="rect",xmin=21532,xmax=30000,ymin=-0.05,ymax=0.05,color=navy,fill=navy)+
  annotate(geom="text",x=23500,y=0,color="white",label="S",fontface='bold')+
  annotate(geom="rect",xmin=25361,xmax=30000,ymin=-0.05,ymax=0.05,color=coral,fill=coral)+
  annotate(geom="text",x=25750,y=0,color="white",label="3a",fontface='bold')+
  annotate(geom="rect",xmin=26213,xmax=30000,ymin=-0.05,ymax=0.05,color=green,fill=green)+
  annotate(geom="rect",xmin=26449,xmax=30000,ymin=-0.05,ymax=0.05,color=purple,fill=purple)+
  annotate(geom="text",x=26700,y=0,color="white",label="M",fontface='bold')+
  annotate(geom="rect",xmin=27017,xmax=30000,ymin=-0.05,ymax=0.05,color=yellow,fill=yellow)+
  annotate(geom="rect",xmin=27364,xmax=30000,ymin=-0.05,ymax=0.05,color=orange,fill=orange)+
  annotate(geom="rect",xmin=27864,xmax=30000,ymin=-0.05,ymax=0.05,color=grey,fill=grey)+
  annotate(geom="rect",xmin=28235,xmax=30000,ymin=-0.05,ymax=0.05,color=aqua,fill=aqua)+
  annotate(geom="text",x=28800,y=0,color="white",label="N",fontface='bold')+
  annotate(geom="rect",xmin=29510,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,fill="white",alpha=0.3)+
  geom_point(alpha=0.8,data=summaryC%>%filter(location=="Gamma")%>%filter(n>20)%>%arrange(n),aes(x=j5,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryC%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j5,y=0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryC%>%filter(location=="Gamma")%>%filter(n>20)%>%arrange(n),aes(x=j3,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryC%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j3,y=0.05,size=m,color=n))+
  theme(
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    axis.line.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    legend.justification = "center",
    legend.direction = "vertical",
    legend.key.size = unit(0.5, "cm"),
    legend.key.height = unit(0.3, "cm"),
        )+
  scale_color_gradient("Number of\nSamples",low=navy,high=coral,limits= c(20,80))+
  annotate(geom="text",label="Gamma",fontface='bold',x=1000,y=-0.5,color="#4D4845", hjust = 0)+
  annotate(geom="text",label="Omicron",fontface='bold',x=1000,y=0.5,color="#4D4845", hjust = 0)+
  scale_size_continuous("Number of\nReads",limits= c(0,180000))
```
  ## Generate noncanonical sgRNAs plot (Delta Omicron)
```{r}
# Noncanonical sgRNA
Delta =read.delim("../../tsv/Delta_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Delta$j5=as.numeric(as.character(Delta$j5))
Delta$j3=as.numeric(as.character(Delta$j3))
Delta$location="Delta"
Delta$y=-0.05

Omicron =read.delim("../../tsv/Omicron_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
Omicron$j5=as.numeric(as.character(Omicron$j5))
Omicron$j3=as.numeric(as.character(Omicron$j3))
Omicron$location="Omicron"
Omicron$y=0.05

VariantD=rbind(Delta,Omicron)

summaryD = VariantD%>%mutate(total=(as.numeric(as.character(count))))%>%group_by(j5,y,location,j3)%>%summarise(n=n(),m=sum(total))

fullD=ggplot(mapping=aes(x=j5,y=y,xend=j3,yend=y))+
  geom_curve(data=summaryD%>%filter(location=="Delta")%>%filter(n>20),lineend = "round",curvature=0.3,color=grey,size=0.1)+
  geom_curve(data=summaryD%>%filter(location=="Omicron")%>%filter(n>20),lineend = "round",curvature=-0.3,color=grey,size=0.1)+
  scale_alpha_continuous("Number of Samples")+
  ft_theme()+
  scale_x_continuous("Position")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=200,ymin=-0.05,ymax=0.05,color="grey30",fill="grey30")+
  annotate(geom="rect",xmin=200,xmax=13483,ymin=-0.05,ymax=0.05,color="grey50",fill="grey50")+
  annotate(geom="text",x=7000,y=0,color="white",label="ORF1a",fontface='bold')+
  annotate(geom="rect",xmin=13483,xmax=30000,ymin=-0.05,ymax=0.05,color="grey60",fill="grey60")+
  annotate(geom="text",x=17000,y=0,color="white",label="ORF1b",fontface='bold')+
  annotate(geom="rect",xmin=21532,xmax=30000,ymin=-0.05,ymax=0.05,color=navy,fill=navy)+
  annotate(geom="text",x=23500,y=0,color="white",label="S",fontface='bold')+
  annotate(geom="rect",xmin=25361,xmax=30000,ymin=-0.05,ymax=0.05,color=coral,fill=coral)+
  annotate(geom="text",x=25750,y=0,color="white",label="3a",fontface='bold')+
  annotate(geom="rect",xmin=26213,xmax=30000,ymin=-0.05,ymax=0.05,color=green,fill=green)+
  annotate(geom="rect",xmin=26449,xmax=30000,ymin=-0.05,ymax=0.05,color=purple,fill=purple)+
  annotate(geom="text",x=26700,y=0,color="white",label="M",fontface='bold')+
  annotate(geom="rect",xmin=27017,xmax=30000,ymin=-0.05,ymax=0.05,color=yellow,fill=yellow)+
  annotate(geom="rect",xmin=27364,xmax=30000,ymin=-0.05,ymax=0.05,color=orange,fill=orange)+
  annotate(geom="rect",xmin=27864,xmax=30000,ymin=-0.05,ymax=0.05,color=grey,fill=grey)+
  annotate(geom="rect",xmin=28235,xmax=30000,ymin=-0.05,ymax=0.05,color=aqua,fill=aqua)+
  annotate(geom="text",x=28800,y=0,color="white",label="N",fontface='bold')+
  annotate(geom="rect",xmin=29510,xmax=30000,ymin=-0.05,ymax=0.05,color="grey80",fill="grey80")+
  annotate(geom="rect",xmin=0,xmax=30000,ymin=-0.05,ymax=0.05,fill="white",alpha=0.3)+
  geom_point(alpha=0.8,data=summaryD%>%filter(location=="Delta")%>%filter(n>20)%>%arrange(n),aes(x=j5,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryD%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j5,y=0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryD%>%filter(location=="Delta")%>%filter(n>20)%>%arrange(n),aes(x=j3,y=-0.05,size=m,color=n))+
  geom_point(alpha=0.8,data=summaryD%>%filter(location=="Omicron")%>%filter(n>20),aes(x=j3,y=0.05,size=m,color=n))+
  theme(
    axis.text.y=element_blank(),
    axis.title.y=element_blank(),
    axis.line.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "right",
    legend.justification = "center",
    legend.direction = "vertical",
    legend.key.size = unit(0.5, "cm"),
    legend.key.height = unit(0.3, "cm"),
        )+
  scale_color_gradient("Number of\nSamples",low=navy,high=coral,limits= c(20,80))+
  annotate(geom="text",label="Delta",fontface='bold',x=1000,y=-0.5,color="#4D4845", hjust = 0)+
  annotate(geom="text",label="Omicron",fontface='bold',x=1000,y=0.5,color="#4D4845", hjust = 0)+
  scale_size_continuous("Number of\nReads",limits= c(0,180000))
```
  ## Summary Output Plot (Fig 4 & Fig 5)
```{r}
Fig4 <- ggarrange(fullA, fullB, fullC, fullD, common.legend = TRUE, ncol = 2, nrow = 2)
ggsave(file.path("./Figure 4. The noncanonical subgenomic RNAs distribution plot from four different variants compared to Omicron variant.pdf"), Fig4, width = 21, height = 14.8, units = "cm")

Fig5 <- ggarrange(Omicron_plot, full, ncol = 1, nrow = 2)
ggsave(file.path("./Figure 5_v2. Profiling of noncanonical subgenomic RNAs form different SARS-CoV-2 Omicron lineages.pdf"), Fig5, width = 21, height = 14.8, units = "cm")
```



### Other Example Code
  ## Generate Top 50 sgRNA from raw noncanonical junction
```{r}
BA.4 = read.delim("../../tsv/BA.4_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")

BA.4 = BA.4%>%mutate(total=(as.numeric(as.character(count))))%>%group_by(JS,j5,j3,deletion.size,evtype,evrelorf)%>%summarise(count=sum(total))%>%arrange(desc(count))%>%head(50)

BA.5 = read.delim("../../tsv/BA.5_sgRNA_nc_junction_summary.tsv", header= TRUE, sep = "\t")
BA.5 = BA.5%>%mutate(total=(as.numeric(as.character(count))))%>%group_by(JS,j5,j3,deletion.size,evtype,evrelorf)%>%summarise(count=sum(total))%>%arrange(desc(count))%>%head(50)
```
  ## Load data (excel)
```{r}
library(openxlsx)
Name <- read.xlsx("$filefullpath/filename.xlsx",sheet = "工作表1")
```
  ## Combine all dataframe
```{r}
Variant = list(B.1.1.7,B.1.351,B.1.617.2,P.1,B.1.1.529)
VariantJS <- Variant %>% reduce(full_join)
##https://www.delftstack.com/zh-tw/howto/r/merge-in-r/
```
  ## sum up by JS
```{r}
B.1.1.7 <- aggregate(count ~ JS , B.1.1.7, sum) 
B.1.1.7 <- filter(B.1.1.7, count >= 100) 
B.1.1.7 <- arrange(B.1.1.7,desc(count))
B.1.351 <- aggregate(count ~ JS , B.1.351, sum) 
B.1.351 <- filter(B.1.351, count >= 100) 
B.1.351 <- arrange(B.1.351,desc(count))
B.1.617.2 <- aggregate(count ~ JS , B.1.617.2, sum) 
B.1.617.2 <- filter(B.1.617.2, count >= 100) 
B.1.617.2 <- arrange(B.1.617.2,desc(count))
P.1 <- aggregate(count ~ JS , P.1, sum) 
P.1 <- filter(P.1, count >= 100) 
P.1 <- arrange(P.1,desc(count))
B.1.1.529 <- aggregate(count ~ JS , B.1.1.529, sum) 
B.1.1.529 <- filter(B.1.1.529, count >= 100) 
B.1.1.529 <- arrange(B.1.1.529,desc(count))
```